### 2017-09-08 paper/related.tex
pass on related work

%\textit{Test selection:}
Regression testing research has focused
mostly on test suite minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012,soetens-etal-2016}.  Most of these
techniques are unsoud (\ie{}, they do not guarantee that
fault-revealing tests will be considered for testing).  The test
selection technique Ekstazi~\cite{ekstazi-web,gligoric-etal-issta2015}
is an example of a sound regression testing technique. It
conservatively computes which tests have been impacted by file
changes.  A test is discarded for execution if it does not depend on
any changed file dynamically reachable from execution.\Comment{ Curiously
Ekstazi's evaluation discovered subjects with parallelism enabled by
default.} \c{C}elik~\etal{}~\cite{celik-etal-fse2017} recently extended
Ekstazi to track files accessed outside JVM boundaries.  Important to
note that regression testing techniques, including test selection, is
complementary to test suite parallelization.

@@

The use of the Simple Instruction Multiple Data (SIMD) design has been
previoulsy explored to accelerate test
execution~\cite{damorim-etal-issta2007,damorim-etal-tse2008,kim-etal-issre2012,nguyen-etal-icse2014,rajan-etal-ase2014,sen-etal-fse2015,yaneva-etal-issta2017}. The
SIMD architecture, as implemented in modern GPUs for instance, allows
the execution of a given instruction simultaneously against multiple
data.  For that reason, in principle, a test could be ran
simulteneously against multiple inputs.  Recent
work~\cite{rajan-etal-ase2014,yaneva-etal-issta2017} explored the
feasibility of testing embedded software using GPUs.  Although
benchmarks indicate superior performance compared to traditional
multicore CPUs, the use of the technology in broader settings is
unfortunately limited. For example, execution of more general programs
can violate SIMD's lock-step assumption on the control-flow of threads
affecting negatively performance. In contrast to the datasets used in
those papers, often each test is associated with a single input
(instead of many).  Furthermore, handling complex data is challenging
in SIMD~\cite{damorim-etal-issta2007,damorim-etal-tse2008}.

>>>>

%ekstazi-web,
Regression testing research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012,soetens-etal-2016}.  Most of these
techniques are unsoud (\ie{}, they do not guarantee that
fault-revealing tests will be considered for testing).  The test
selection technique
Ekstazi~\cite{gligoric-etal-issta2015,celik-etal-fse2017} is an
example of a sound regression testing technique. It conservatively
computes which tests have been impacted by file changes.  A test is
discarded for execution if it does not depend on any changed file
dynamically reachable from execution.\Comment{ Curiously Ekstazi's
  evaluation discovered subjects with parallelism enabled by
  default.}\Comment{ \c{C}elik~\etal{}~\cite{} recently extended
  Ekstazi to track files accessed outside JVM boundaries.} Important
to note that regression testing techniques, including test selection,
is complementary to test suite parallelization.

@@

The use of the Single Instruction Multiple Data (SIMD) design has been
previoulsy explored in research to accelerate test
execution~\cite{damorim-etal-issta2007,damorim-etal-tse2008,kim-etal-issre2012,nguyen-etal-icse2014,rajan-etal-ase2014,sen-etal-fse2015,yaneva-etal-issta2017}. The
SIMD architecture, as implemented in modern GPUs, for instance, allows
the execution of a given instruction simultaneously against multiple
data.  For that reason, in principle, one test could be ran
simulteneously against multiple inputs provided that multiple test
inputs exist associated to that one test.  Recent
work~\cite{rajan-etal-ase2014,yaneva-etal-issta2017} explored that
idea to speedup test execution of embedded software using graphic
cards. Although benchmarks indicate superior performance compared to
traditional multicore CPUs, the use of the technology in broader
settings is limited. For example, execution of more general programs
can violate the SIMD's lock-step assumption on the control-flow of
threads.  This violation would affect negatively performance.
Furthermore, handling complex data is challenging in
SIMD~\cite{damorim-etal-issta2007,damorim-etal-tse2008}.  The approach
is promising when multiple input vectors exist for each test and the
testing code heavily manipulates scalar data types.  The datasets used
in those papers satisfied those constraints.
